Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-06-01 EMNLP-demo-paper/conclusion.tex
grammar fix

Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such neural machine translation and more.

>>>>

Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such as neural machine translation and more.
